Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models By Using Data of Pollsters From Five Thirty Eight In 2024

### 2024-10-22 paper/paper.qmd
title changed

---
title: "Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: https://github.com/zzq20010617/2024_USelection_prediction"
date: today
date-format: long
abstract: "This paper presents a multiple linear regression model for forecasting the outcome of the 2024 U.S. Presidential Election. Using nationwide polling data, we predict the percentage of support for U.S. presidential candidates based on key factors such as sample size, pollster quality, and timing. Our model aggregates these predictions to simulate potential election outcomes. The results reveal how specific poll attributes affect the accuracy of forecasts, offering valuable insights for predicting the likelihood of various electoral scenarios."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---

>>>>

---
title: "Forecasting the US Presidential Election: A Poll-of-Polls Approach Using Linear Models By Using Data of Pollsters From Five Thirty Eight In 2024"
author: 
  - Ziqi Zhu
  - Yuanchen Miao
  - Claire Chang
thanks: "Code and data are available at: https://github.com/zzq20010617/2024_USelection_prediction"
date: today
date-format: long
abstract: "This paper presents a multiple linear regression model for forecasting the outcome of the 2024 U.S. Presidential Election. Using nationwide polling data, we predict the percentage of support for U.S. presidential candidates based on key factors such as sample size, pollster quality, and timing. Our model aggregates these predictions to simulate potential election outcomes. The results reveal how specific poll attributes affect the accuracy of forecasts, offering valuable insights for predicting the likelihood of various electoral scenarios."
number-sections: true
bibliography: references.bib
format:
  pdf:
    toc: true
    number-sections: true
    colorlinks: true
---
